Visual Inference for Networks

### 2016-07-14 JSM/VizInfSlides.Rmd
more sliding
model slides

@@

@@

>>>>

## Model Parameters

Effect name | Parameter | Corresponding Statistic
------------|-----------|-------------------------
Rate 1 (wave 1 $\rightarrow$ 2) | $\alpha_1$ | $\sum\limits_{i,j = 1 i \neq j}^n (x_{ij}(t_2) - x_{ij}(t_1))^2$  
Rate 2 (wave 2 $\rightarrow$ 3) | $\alpha_2$ | $\sum\limits_{i,j = 1 i\neq j}^n (x_{ij}(t_3) - x_{ij}(t_2))^2$
Outdegree | $\beta_1$ | $s_{i1}(x) = \sum\limits_{j=1}^n x_{ij}$ 
Reciprocity | $\beta_2$ | $s_{i2}(x) = \sum\limits_{j=1}^n x_{ij}x_{ji}$ 
Jumping Transitive Triplets | $\beta_3$ | $s_{i3}(x) = \sum\limits_{\forall j\neq h} x_{ij}x_{ih}x_{hj} \mathbb{I}(v_i = v_h \neq v_j)$

@@

R Simulation Investigation for Empirical Network Analysis

Method of moment Monte Carlo estimation of the parameters in models

@@

Help to find a measure of difficulty of a lineup
